
\begin{flushleft}
AALTO YLIOPISTO \hfill BACHELOR'S THESIS \\
PERUSTIETEIDEN KORKEAKOULU \hfill ABSTRACT \\
PL 11000 \\
00076 AALTO \\
\end{flushleft}

\begin{minipage}{15cm}
\begin{framed}
    Author: Ville Kumpulainen \\
    Title: Adopting agile software development in large organizations \\
    Program: Information Networks \\
    Date: 15.9.2017 \\
        Page count:~\pageref{LastPage} \\
        Responsible teacher: Miia Jaatinen \\
        Supervisor: Maria Paasivaara \\
        Language: English
\end{framed}
\end{minipage}

\bigskip

{\large\bfseries Abstract: \par} Agile methods have increased their
popularity among software development companies, but adopting them
in a large organization has not been and still is not easy nor
straightforward. I conducted a systematic literature review on why large
organization adopt lean and agile software development methodologies and
how these transformation proceed. The keyword search found 1182 unique
papers on the subject. Using a specific inclusion criteria, 6 of these
papers were included in the final analysis. These papers represented
the highest quality regarding their informativeness and narrative of
the agile transformation process. The analysis of these papers revealed
four major categories of reasons for the agile transformation: Business,
process, management and organizational reasons. The most significant
reasons were excess process overhead due to waterfall development and
the need to deliver software faster. Most transformations started from
an executive management decision and proceeded in a planned, step-wise
fashion.

\medskip

\begin{minipage}{15cm}
\begin{framed}
        Keywords: Agile software development, large-scale agile, organizational
        transformation, adopting agile software development
\end{framed}
\end{minipage}
