Agile software development is a collection of methods describing an
alternative for traditional software development methods. The fundamental
idea is to build software iteratively in small increments while
constantly adapting the software according to customer feedback.
Feedback is acquired by delivering software to the customer already in
the early phases of development. With constant customer involvement
changes can be made rapidly even late in development. These principles were
explained in the ``agile manifesto'' [2].

According to Mohammed and Abushama [7], some of the most popular agile
methods in the industry are extreme programming and Scrum. Scrum is a
software development process for small teams that focuses on project
management. A scrum team develops a software product in short sprints,
which last from 1 to 4 weeks. In each sprint, the team implements,
tests, reviews and ships a finished piece of software [8]. A sprint is
strictly timeboxed and the end date typically does not change. If the
team cannot finish what they originally planned to during the sprint,
the delivered functionality can be reduced, but the length of the sprint
always remains the same.

Extreme programming (XP) is a collection of practices that emphasize
on concurrent planning, implementing, testing and analyzing [1]. The
aim is to enable efficient incremental and iterative development
using e\.g\. continuous feedback from customer, test driven development
and continuous integration. Other important practices include pair
programming and constant refactoring [1].
