During the transformation, all organizations invested in communicating
the new process and providing training on the subject. In all
organizations most people were new to agile, so the prerequisite for the
transformation is to provide necessary training on the new model before
actually starting the transformation.

Most organizations organized some sort of training as the very first
step to the transformation. For example, Anwar et al had reported
finding classroom training as the proper option for their needs. This
training covered the core concepts of agile, an overview of Scrum (which
is the method the company was adopting), release and sprint planning,
retrospectives and user story writing. [P1]

Ayed et al had conducted questionnaires to their personnel to identify
the most important training needs for their organization. As the
transformation in this company had started from the bottom, the software
delivery team had a decent understanding of agile to begin with.
However, they still organized two half-day training sessions. [P2]

At Ericsson, the transformation was conducted in a rather slow manner.
The company first spent half a year to spread knowledge of Agile
software development methods before fully launching the transformation.
This was found necessary, as the software development organization at
Ericsson was the largest of the primary studies, and therefore the
transformation being the most complex one. In order to successfully
carry out the transition, they wanted to solve all major problems
beforehand. [P3]

The Agile Office at Samsung Electronics first organized training
sessions for agile coaches and Scrum masters, who were then distributed
to each software development team. The whole software delivery personnel
in that company was simply too large to train simultaneously. The agile
coaches then supported the Scrum masters in training their respective
teams to follow agile methods in their daily work. [P4]

Roman et al reported that their organization approached agile
training from top-down as well. Management, development leads and
architects promoted discussion on agile, held debate sessions and gave
presentations on related topics to increase knowledge on agile methods:
\textit{``Local presentation sessions to all members of a certain office
were organized to take place world-wide in the same week in which teams
already going through the transition were motivated to report their
experience to others as a way to encourage the adoption of agile and to
share good practices''}. [P5, p.3]
