This paper makes a contribution to recent research regarding large-scale
agile transformations. While previous research has extensively covered
the usage of agile methods in small, medium and large organizations,
the transformations in especially large organizations have not been
covered very broadly. This paper compiles reported large-scale agile
transformations from past four years creating a summary of recent
research data to be used by practitioners and researchers alike.

The first goal of this paper was to find the most typical reasons behind
large organizations undertaking agile transformations. The main reason
for moving to agile methods was to increase collaboration inside the
organization, followed by the need to respond better to changing markets
and change requests. Software development using waterfall methods
caused the organization to structure itself into specialized silos by
functionality, so that software developers are one team, designers one
team and QA is a separate team. Most organizations found that using
agile methods and cross-functional teams they were able to ship features
faster and reduce rivalry and unnecessary competition between teams.

The secondary goal was to cover what measures these organizations take
in order to succeed in this transformation in which most companies
struggle. Most transformations proceeded in a planned, step-wise manner.
They began with research and training, followed by a pilot project or
two and finally resulting in company-wide roll-out to agile methods.
Furthermore, the transformations were initiated by top management as
a response to dissatisfaction with the current process and state of
business.

This paper provided answers to how large-scale agile transformations
proceed, but it did not provide insight on what happened to the
organizations after the transformation was complete. Future research
could focus on how organizations evolve their agile methods after the
initial adoption, are they able to maintain agility over time and what
kind of long term effects the transformation causes.
