
Due to the research questions and the primary focus of this study, there are
four different aspects to guide the inclusion and exclusion criteria:
\textit{agile software development, organizational transformation, large-scale
and empirical}. Table I lists these aspects and examples of relevant and
non-relevant topics related to each aspect.

\input{table1.tex}
\vspace{1.5cm}

Agile software development as an aspect covers studies focusing on
software development organizations that apply agile methodologies in
their work. This immediately excludes all other applications of agile
methods than software development.

Organizational transformation asserts that primary studies are required
to provide insight on organizational transformation, specifically
concerning the research questions, i.e. how and why organizations
migrate from traditional processes to agile methods. This excludes
studies that e.g. compare traditional and agile methods or describing
how agile methods are used in an organization but not covering the
introduction of the methods. Studies that do not explicitly present how
the large-scale agile transformation proceeds are not included in this
review.

The third aspect states that included studies must conform to the
previously set limits. Some papers do not clearly state the size of the
software development organization. Merely stating that the organization
is large but not stating the actual size resulted in exclusion of the
paper. Moreover, adopting large-scale agile methods has to include the
whole organization adopting the methods. If only one team or some part
of the organization, but not the whole organization, adopted agile
methodologies in their work, the paper was excluded.

The final aspect excludes hypothetical and theoretical models
and papers, the included studies must present real world cases.
Textbooks and theoretical models concerning large-scale agile software
development were excluded from this study, as the goal is to observe
actual experiences. Also, studies that only report the advantages or
limitations of adopting large-scale agile were excluded, since this
paper studies the transformation process itself, not the results.

Finally, primary studies must include at least some discussion on
all aforementioned aspects. However, even if they contain some other
non-relevant discussion they can still be included, and the relevant
parts of the study will be used.
