\noindent [1] Beck, K., 1999. Embracing change with extreme programming, Computer,
32(10):70–77

\noindent [2] Beck, K., et al. 2001. ``The Agile Manifesto''.
http://agilemanifesto.org/

\noindent [3] Boehm, B., Turner, R., 2005. Management challenges to implementing agile
processes in traditional development organizations. IEEE Software.\ 22(5), p. 30–39

\noindent [4] Cohn, M., Ford, D., 2003. Introducing an agile process to an
organization Computer. 36 (6), 74–78.

\noindent [5] Dikert, K., Paasivaara, M., Lassenius, C., 2016. Challenges and success factors
for large–scale agile transformations: A systematic literary review. The journal
of Systems and Software.\ p. 87–108.

\noindent [6] Kitchenham, B. A., Guidelines for performing systematic literature
reviews in software engineering. Technical report EBSE–2007–01, Keele University
Technical Report, 2007

\noindent [7] Mohammed, A.M., Abushama, H.M., 2013. Popular agile approaches in software
development: Review and analysis. In Computing, Electrical and Electronics
Engineering (ICCEEE), 2013 International conference on. IEEE, 2013

\noindent [8] Rising, L., Janoff, N.S., 2000. The Scrum software development process for small teams. IEEE Software.\ p. 26–32

\noindent [9] Fowler, M. 2006. ``Continuous integration''.
https://martinfowler.com/articles/continuousIntegration.html

\noindent [10] Dyba T., Dingsøyr T., 2008 Empirical studies of agile
software development: A systematic review. The journal of Systems and
Software.\ 50 (8-9) p. 833–859.

\noindent [11] Lindvall M., Muthig D., Dagnino A., Wallin C.,
Stupperich M., Kiefer D., May J., Kahkonen T., 2004
Agile software development in large organizations, Computer 37 (12) p. 26–34

\noindent [12] Dikert K., Paasivaara M., Lassenius C., 2015, Adopting agile software development in large organizations: A systematic literature review, unpublished manuscript
